---
title: "CLT Explain"
format: revealjs
editor: visual
---

# Central Limit Theorem

## CLT

What is Central Limit Theorem ?

## Measurement of Central Tendency 

dafsa

## Measurement of Dispersion 

## Bullets

When you click the **Render** button a document will be generated that includes:

-   Content authored with markdown
-   Output from executable code
-   

## Code

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
# Sample data
data <- c(12, 15, 18, 21, 24, 27, 30, 33, 36, 39)

# Calculate mean, median, and mode
mean_value <- mean(data)
median_value <- median(data)
mode_value <- as.numeric(names(sort(table(data), decreasing = TRUE)[1]))

```

```{r}
# Calculate variance and standard deviation
variance_value <- var(data)
sd_value <- sd(data)



```

```{r}
# Visualize distribution
hist(data, main = "Histogram of Sample Data", xlab = "Value", ylab = "Frequency", col = "lightblue")
abline(v = mean_value, col = "red", lwd = 2)
abline(v = median_value, col = "blue", lwd = 2)
legend("topright", legend = c("Mean", "Median"), col = c("red", "blue"), lwd = 2)


```

```{r}
# Simulate CLT
set.seed(123)  # For reproducibility
n_samples <- 1000
sample_means <- numeric(n_samples)

for (i in 1:n_samples) {
  sample_data <- base::sample(data, size = 10, replace = TRUE)
  sample_means[i] <- mean(sample_data)
}

# Plot the histogram of sample means
hist(sample_means, main = "Histogram of Sample Means (CLT)", xlab = "Sample Mean", ylab = "Frequency", col = "lightgreen")

```
